Efficient Feasibility Checking Algorithm of Photovoltaic Array Reconfiguration

### 2019-12-03 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-03 17-28-03

For several series connected PV cells, shaded or damaged cell causing normal cells to produce higher voltages that may reverse bias of ``bad'' cells.
When a large number of series connected cells cause a huge reverse bias across shaded cells, leading to large dissipation of energy in the ``bad'' cells.
This huge energy dissipation occurring in a small area might get overheating or burning of PV cells, or ``hot-spots''.
To protect PV cells from ``hot-spots'', bypass diode is used to circumvent concentrated energy dissipation.
However, the operation of bypass diode will cause several stop delivering power and generate multiple local maximum power points\cite{Orozco-Gutierrez2016}.
Furthermore, strand bypass diode can not complete eliminate hot-spotting\cite{kim2015reexamination}.

@@

Another attractive direction to improve PV system efficiency under different working condition is PV reconfiguration.

>>>>

For several series connected PV cells, shaded or damaged cell causing normal cells to produce higher voltages that may reverse bias of ``bad'' cells.
When a large number of series connected cells cause a huge reverse bias across shaded cells, leading to large dissipation of energy in the ``bad'' cells.
This huge energy dissipation occurring in a small area might get overheating or burning of PV cells, or ``hot-spots''.
To protect PV cells from ``hot-spots'', bypass diode is used to circumvent concentrated energy dissipation.
However, the operation of bypass diode will cause several stop delivering power and generate multiple local maximum power points\cite{Orozco-Gutierrez2016} or the total PV module current are limited by the one of worst ``bad'' cell.
In both situation, available energy is lost.
Furthermore, strand bypass diode can not complete eliminate hot-spotting\cite{kim2015reexamination}.

@@

Another attractive direction to improve PV system efficiency under different working condition is the reconfiguration of PV arrays.
This concept was first proposed by Salameh $et$ $al.$\cite{Salameh1990} in 1990.
Then in 2002, Sherif and Boutros $et$ $al.$ proposed a reconfigurable scheme for PV arrays that using transistors as switch network to improve performance\cite{sherif2002solar}.
